### 2016-05-20 paper/paper.tex
Adding a little clarification

Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
malicousness inherent to the currency's design.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
when miners have different bandwidth to a given endpoint at a level beyond their direct 
control. In prior cryptocurrencies, the proof-of-work uses resources entirely under the
miner's control. The extreme of having a unique position to attack a site is being the
target, and having the private key for the site. Having this priveleged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

@@

\shrug

>>>>

Many positive results have come from cryptocurrencies.
Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
malicousness inherent to a currency's design, turning the notion of what constitutes
a ``useful'' proof-of-work on its head. Certainly a DDoS attack it useful to someone,
but negatively impacts society as a whole.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
when miners have different bandwidths to that given endpoint. The extreme of 
having a different bandwidth is being the target, and having the private key 
for the site. Having this priveleged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

@@
